%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Assistant Project Manager} % Job title
    {Indian Institute of Technology Bombay} % Organization
    {Mumbai, India} % Location
    {Jan. 2018 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Overall coordinator of research carried using DWSIM \& OpenModelica.}
        \item {Guiding the other team members working to develop chemical process simulator in OpenModelica.}
        \item {Report the monthly progress of work carried out in DWSIM and OpenModelica to MHRD, Goverment of India.}
        \item {Coordinating all the external activities to promote the use of DWSIM and OpenModelica for academic and research based activities in other colleges in India.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Project Research Assistant} % Job title
    {Indian Institute of Technology Bombay} % Organization
    {Mumbai, India} % Location
    {Sep. 2016 - Dec. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed of steady state unit operations for chemical process simulation in OpenModelica.}
        \item {Developed of thermodynamic models \& functions for chemical process simulation in OpenModelica.}
        \item {Developing scripts for creating spoken tutorial on DWSIM and OpenModelica.}
        \item {Review textbook companions (TBCs) created in OpenModelica.}
        \item {Review flowsheets created in DWSIM.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Faculty of Mathematics} % Job title
    {T.I.M.E} % Organization
    {New Delhi, India} % Location
    {Sep. 2015 - Aug. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Taught trigonometry, differential \& integral calculus for JEE aspirants.}
        \item {Taught quantitative ability (QA) for MBA aspirants.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Associate System Engineer} % Job title
    {IBM India Pvt. Ltd.} % Organization
    {Bangalore, India} % Location
    {Aug. 2014 - Sep. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Lead for regression testing of Bell Canada web application.}
        \item {Responsible for contribution to Automation testing framework development.}
        \item {Engaging in calls with developers to get the bug fixed and providing updates to  Project Managers.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
