%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Academic Projects/Internship}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Chemical Engineering \& Process Development Division, National Chemical Laboratory} % Organization
    {Process Development for Continuous Manufacture of Pendimethalin} % Project title
    {Pune, India} % Location
    {Dec. 2013 - Apr. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Guide: \textbf{Dr. Vivek V Ranade} (Deputy Director \& Chair).}
        \item {Develop process flow diagram for continuous manufacture of Pendimethalin.}
        \item {Perform material and energy balance to find the chemical and energy requirement required to produce 220 kg/hr.}
        \item {Design the suitable unit operations as required for the operation of the plant for the desired capacity.}
        \item {Perform economic evaluation for the complete plant capacity to find the payback period.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {School of Chemical \& Biotechnology, SASTRA University} % Organization
    {Adsorption of Methylene Blue on Chrysopogon Zizanioides} % Project title
    {Thanjavur, Tamil Nadu, India} % Location
    {Jan. 2013 - Apr. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Guide: \textbf{Dr. V. Ponnusami} (Associate Professor).}
        \item {To study the kinetics parameters and different curves like temperature and pressure effect, adsorption isotherm when methylene blue is adsorbed on chrysopogon zizaniodes.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
